PEACE: {\underline P}arallel {\underline E}nvironment for {\underline A}ssembly and {\underline C}lustering of Gene {\underline E}xpression

### 2010-04-19 papers/NAR_web_server_2009/paper.tex
Modifications to paper; addition of natbibOrig.sty file

\mc{In applying the tools to real data Sanger data, we used the Human
Benchmark Dataset used to test \easycluster\/ \cite{Picardi09}, and
the A076941.fa {\it Arabidopsis thaliana} dataset used to test WCD
\cite{Hazelhurst08,Hazelhurst08a}, with results in
Table~\ref{SangerReal}.  We notice essentially identical
results for PEACE and WCD in quality, both significantly better than
Cap3 in Sensitivity and Type 1 error rate, while slightly worse in the
Jaccard Index and Type 2 error.  In runtime we see some inconsistency,
with PEACE showing a 60\% runtime improvement in the smaller dataset,
requiring 20\% more time in the Arabidopsis dataset.}

\begin{table*}[tbp]
\begin{center}
\begin{tabular} {| c || c || c | c | c | c | c | c | c |}
\hline
 & 
& Sensitivity & Jaccard & \begin{tabular}{c} Type 1 \\
  error \end{tabular} & \begin{tabular}{c} Type 2 \\
  error \end{tabular} &
\begin{tabular}{c} Number \\ of  \\
    Clusters \end{tabular} & \begin{tabular}{c} Number \\ of \\
    Singletons \end{tabular}
    & \begin{tabular}{c} Single \\ processor \\ runtime (s) \end{tabular}\\
\hline EasyCluster Human & \peace & 0.998 & 0.672 & 0.153 & 0.042 & 118 & 21 & 293 \\
\cline{2-9} Benchmark & \wcd & 0.998 & 0.672 & 0.144 & 0.044 & 113 & 16 & 804 \\
\cline{2-9} (111 Genes) & \capthree & 0.657 & 0.643 & 1 & 0.001 & 2269 & 1827 & \mbox{NA} \\
\hline
\hline WCD A076941 & \peace & 0.932 & 0.475 & 0.351 & 0.027 & 18825 & 8951 & 1166\\
\cline{2-9} Benchmark & \wcd & 0.933 & 0.476 & 0.350 &  0.027 & 18787 & 8553 & 966 \\
\cline{2-9} (13240 genes) & \capthree & 0.826 & 0.802 & 0.486 & 0.014 & 25042 & 14916 &
\mbox{NA} \\
\hline
\end{tabular}
\label{SangerReal}
\end{center}
\caption{Comparisons of runs on the EasyCluster human Benchmark
  Dataset and the WCD A076941 Arabidopsis thaliana dataset using the
  standard quality measurments.}
\end{table*}

@@

>>>>

\mc{In applying the tools to real data Sanger data, we used the Human
Benchmark Dataset used to test \easycluster\/ \cite{Picardi09}, and
the A076941.fa {\it Arabidopsis thaliana} dataset used to test WCD
\cite{Hazelhurst08,Hazelhurst08a}, with results in
Table~\ref{SangerReal}.  We notice essentially identical
results for PEACE and WCD in quality, both significantly better than
Cap3 in Sensitivity and Type 1 error rate, while slightly worse in the
Jaccard Index and Type 2 error.  In runtime we see some inconsistency,
with PEACE showing a 60\% runtime improvement in the smaller dataset,
requiring 20\% more time in the Arabidopsis dataset.  In Section~D.1
of the Supplementary Materials we present runtimes several more
sets, observing that while \peace\/ appears to be significantly more
faster on the smaller sets, \wcd\/ does overtake it for larger sets.

\begin{table*}[tbp]
\begin{center}
\begin{tabular} {| c || c || c | c | c | c | c | c | c |}
\hline
 & 
& Sensitivity & Jaccard & \begin{tabular}{c} Type 1 \\
  error \end{tabular} & \begin{tabular}{c} Type 2 \\
  error \end{tabular} &
\begin{tabular}{c} Number \\ of  \\
    Clusters \end{tabular} & \begin{tabular}{c} Number \\ of \\
    Singletons \end{tabular}
    & \begin{tabular}{c} Single \\ processor \\ runtime (s) \end{tabular}\\
\hline
\hline EasyCluster Human & \peace & 0.998 & 0.672 & 0.153 & 0.042 & 118 & 21 & 293 \\
\cline{2-9} Benchmark & \wcd & 0.998 & 0.672 & 0.144 & 0.044 & 113 & 16 & 804 \\
\cline{2-9} (111 Genes) & \capthree & 0.657 & 0.643 & 1.000 & 0.001 & 2269 & 1827 & \mbox{NA} \\
\hline
\hline WCD A076941 & \peace & 0.932 & 0.475 & 0.351 & 0.027 & 18825 & 8951 & 1166\\
\cline{2-9} Benchmark & \wcd & 0.933 & 0.476 & 0.350 &  0.027 & 18787 & 8553 & 966 \\
\cline{2-9} (13240 genes) & \capthree & 0.826 & 0.802 & 0.486 & 0.014 & 25042 & 14916 &
\mbox{NA} \\
\hline
\end{tabular}
\label{SangerReal}
\end{center}
\caption{Comparisons of runs on the EasyCluster human Benchmark
  Dataset and the WCD A076941 Arabidopsis thaliana dataset using the
  standard quality measurments.}
\end{table*}

@@

\mc{We tested the three tools on short-read data using the MetaSim tool of
{\it Richter et al.} [\cite{Richter2008}].  Encoded into MetaSim are
modules configured to emulate the outpspecific tecnology,
including the 454 and Illumina sequences.  For 454, the simulator  }
